Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-03-04 paper/main.tex
abstract polished

\begin{abstract}
  \emph{Transition-based Emerson-Lei automata (TELA)} become a popular
  formalism that generalizes many traditional kinds of automata over
  infinite words including Büchi, co-Büchi, Rabin, Streett, and parity
  automata. Transitions in a TELA are labelled with acceptance marks
  and its accepting formula is a positive Boolean combination of terms
  saying that a particular mark has to be visited infinitely or
  finitely often. % in an accepting run.
  Algorithms processing these automata are often very sensitive to the
  number of %different
  acceptance marks. We introduce a new technique reducing the number
  of %different
  acceptance marks in TELA with use of \emph{quantified Boolean
    formulas (QBF)}.
  % : if a constructed QBF formula is satisfiable then
  % its model encodes an equivalent accepting formula with less
  % acceptance marks.
  In fact, we present three formula constructions
  trading speed for higher reduction
  efficiency. We evaluated our reduction technique on TELA produced by
  state-of-the-art tools Delag, ltl3tela, Rabinizer~4, and Spot. The
  technique reduced some acceptance marks in automata produced by all
  these tools. In the case of Rabinizer~4, the cumulative number of
  acceptance marks was reduced to less than one half. \todo{Sazet ltl3tela a jine tooly vsude jako \texttt{ltl3tela} apod?}
\end{abstract}

>>>>

\begin{abstract}
  \emph{Transition-based Emerson-Lei automata (TELA)} become a popular
  formalism that generalizes many traditional kinds of automata over
  infinite words including Büchi, co-Büchi, Rabin, Streett, and parity
  automata. Transitions in a TELA are labelled with acceptance marks
  and its accepting formula is a positive Boolean combination of terms
  saying that a particular mark has to be visited infinitely or
  finitely often. % in an accepting run.
  Algorithms processing these automata are often very sensitive to the
  number of %different
  acceptance marks. We introduce a new technique reducing the number
  of %different
  acceptance marks in TELA with use of \emph{quantified Boolean
    formulas (QBF)}.
  % : if a constructed QBF formula is satisfiable then
  % its model encodes an equivalent accepting formula with less
  % acceptance marks.
  In fact, we present three formula constructions trading speed for
  higher reduction efficiency. We evaluated our reduction technique on
  TELA produced by state-of-the-art tools of the libraries Owl and
  Spot and by the tool \texttt{ltl3tela}. The technique reduced some
  acceptance marks in automata produced by all the tools. The achieved
  reduction on automata produced by tools of the Owl library was
  between 30 and 40\%.
\end{abstract}
